---
title: "A7: Survey Report"
author: "InflatablePizza"
date: "May 11, 2017"
output: html_document
---

```{r setup, include=FALSE}
setwd("C:/Users/Austin Quach/Google Drive/College/Sophomore/Info 201/Homework/a7-collaboration-inflatablepizza")
survey <- read.csv("data/intro-survey.csv")
source("./scripts/summary.R")
source("scripts/chart1.R")
source("scripts/chart2.R")
source("scripts/chart3.R")
library(cowplot)
num.freshmen <- GetNumPeopleByClassStanding(survey, "Freshman")
num.sophomores <- GetNumPeopleByClassStanding(survey, "Sophomore")
num.juniors <- GetNumPeopleByClassStanding(survey, "Junior")
num.seniors <- GetNumPeopleByClassStanding(survey, "Senior")
never.used.r <- PercentWithRExperience(survey, "Never used it")
used.a.few.times.r <- PercentWithRExperience(survey, "Have used it a few times")
intermediate.user.r <- PercentWithRExperience(survey, "Intermediate user")
percent.mac <- PercentPeopleUseOperatingSystem(survey, "Mac")
percent.windows <- PercentPeopleUseOperatingSystem(survey, "Windows")

```
##Survey Summary
There are a total of `r num.freshmen` freshmen, `r num.sophomores` sophomores, `r num.juniors` juniors, and `r num.seniors` seniors in the class. `r never.used.r`% of people in the class have never used R before, `r used.a.few.times.r`% of people in the class have used R a few times before, and `r intermediate.user.r`% are intermediate users of R. `r percent.mac`% of people typically use Mac operating system while `r percent.windows`% of people typically use Windows operating system.
 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggdraw(Chart1(survey))
ggdraw(Chart2(survey))
ggdraw(Chart3(survey))
```